%-------------------------
% Resume in LaTeX
% Author: Stephen Syl-Akinwale
% Based on a template by Jake Gutierrez (MIT License)
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\usepackage[sfdefault]{FiraSans}
\usepackage[default]{sourcesanspro}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated PDF is machine readable / ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
  \textbf{\Huge \scshape Stephen Syl-Akinwale} \\ \vspace{1pt}
  \small
  \href{mailto:stephensylak@gmail.com}{\underline{stephensylak@gmail.com}} $|$
  \href{https://github.com/stphnmade}{\underline{github.com/stphnmade}} $|$
  \href{https://linkedin.com/in/stephen-syl-akinwale}{\underline{linkedin.com/in/stephen-syl-akinwale}} $|$
  {\underline{+1 (716)-292-5784}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Cornell University}{Ithaca, NY}
    {Bachelor of Arts in Information Science (Concentration in Data Science, Interactive Technology and User Experience)}{May 2025}
    \resumeItemListStart
      \resumeItem{Relevant Coursework: Computing using Python, Object-Oriented Programming \& Data Structures, Functional Programming, Data Visualization, Rapid Prototyping, Learning Analytics, Data-Driven Web Development}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Co-President}{May 2021 -- Sep. 2025}
    {Cornell Music Production}{Ithaca, NY}
    \resumeItemListStart
      \resumeItem{Automated event scheduling workflows with \textbf{Airtable}, boosting event coordination efficiency by 40\%.}
      \resumeItem{Directed marketing and recruitment campaigns, expanding active membership from \textbf{27 to 270+} students.}
      \resumeItem{Materialized club members' visions to produce \textbf{3 multi-genre albums} launched across licensing platforms.}
    \resumeItemListEnd

  \resumeSubheading
    {IT Technician}{Mar. 2026 -- Present}
    {Kaleida Health}{Buffalo, NY}
    \resumeItemListStart
      \resumeItem{Performed \textbf{device imaging and re-imaging} using USB and \textbf{PXE booting}, replacing and upgrading workstations with standardized Kaleida Health builds.}
      \resumeItem{Configured and supported clinical hardware, including \textbf{print servers, label printers, barcode scanners, and multi-monitor workstations} in healthcare environments.}
      \resumeItem{Delivered hands-on \textbf{end-user support} for 15+ staff per site, assisting with \textbf{Office 365, OneDrive, email profile setup}, and secure system access post-migration.}
      \resumeItem{Troubleshot \textbf{network and endpoint issues}, including printer connectivity, Wi-Fi disruptions, and peripheral failures in exam rooms and clinical workstations.}
      \resumeItem{Documented and tracked \textbf{device lifecycle data} (asset tags, serial numbers, user assignments, and deployment status) to ensure accurate migration records and audit readiness.}
      \resumeItem{Collaborated with \textbf{field services engineers, network teams, and project managers} to execute structured deployment playbooks and meet aggressive rollout timelines.}
      \resumeItem{Supported \textbf{infrastructure standardization efforts} across Kaleida Health entities, improving system consistency and reliability ahead of enterprise EMR integration.}
      \resumeItem{Maintained \textbf{SLA compliance} by validating post-deployment functionality, resolving user issues, and ensuring operational stability in high-impact clinical settings.}
    \resumeItemListEnd

  \resumeSubheading
    {IT Technical Support}{Sep. 2023 -- May 2025}
    {eCornell}{Remote / Ithaca, NY}
    \resumeItemListStart
      \resumeItem{Provided front-line technical support for 5,000+ global users, resolving 95\% of tickets within SLA through \textbf{Jamf}, \textbf{Google Admin}, \textbf{Salesforce}, and TDX.}
      \resumeItem{Analyzed crash patterns, optimized system uptime by 18\%, and reduced ticket backlog by 22\% through automation of SQL database queries and Excel-based reporting dashboards.}
      \resumeItem{Collaborated cross-functionally to improve onboarding workflows, decreasing average new-user setup time by 30\%.}
      \resumeItem{Delivered in-person and remote desktop support across Windows, macOS, and mobile platforms, improving end-user satisfaction ratings.}
    \resumeItemListEnd

  \resumeSubheading
    {Program Space Manager (Just About Music -- Program House)}{Jun. 2021 -- Aug. 2023}
    {Cornell University}{Ithaca, NY}
    \resumeItemListStart
      \resumeItem{Reactivated and managed a residential program space following COVID shutdowns, restoring in-person programming, technical access, and event operations for student organizations.}
      \resumeItem{Trained and supported undergraduates on professional audio workflows, including gain staging, microphone setup, recording techniques, and safe operation of studio and live-sound equipment.}
      \resumeItem{Provided hands-on instruction in digital audio tools such as \textbf{Logic Pro} and \textbf{FL Studio}, enabling students to record, edit, and produce audio independently.}
      \resumeItem{Coordinated sound setup and technical support for open mics, showcases, and contracted events with other campus clubs, handling microphones, mixers, speakers, and presentation equipment.}
      \resumeItem{Collaborated with residential managers and student leaders to plan events, manage schedules, and ensure compliance with space usage and safety guidelines.}
      \resumeItem{Tracked equipment inventory and managed budgets using \textbf{Excel}, replacing damaged gear and procuring new materials to maintain operational readiness.}
    \resumeItemListEnd

  \resumeSubheading
    {Sales Development Representative}{Jun. 2023 -- Aug. 2023}
    {AT\&T}{Buffalo, NY}
    \resumeItemListStart
      \resumeItem{Delivered consultative sales support for AT\&T products and services, identifying customer needs and recommending tailored wireless and broadband solutions.}
      \resumeItem{Increased device upgrade conversions by clearly communicating value propositions of new plans, features, and bundled services.}
      \resumeItem{Consistently met or exceeded monthly sales targets while maintaining high customer satisfaction ratings.}
      \resumeItem{Leveraged promotional pricing and in-store incentives to optimize customer savings and drive revenue growth.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{CURide – Community Ridesharing Platform} \emph{\textbar{} Figma, Balsamiq, UX Research, Google Sheets, Agile}}
    {Oct. 2024 -- Dec. 2024}
    \resumeItemListStart
      \resumeItem{Addressed affordability and safety gaps in student transportation at Cornell by designing a ridesharing platform tailored to campus needs.}
      \resumeItem{Led a user-centered redesign after interviewing 12 students to uncover trust, role clarity, and scheduling pain points.}
      \resumeItem{Translated interview insights into low-fidelity \textbf{Balsamiq} wireframes and high-fidelity \textbf{Figma} prototypes, iterating across 3 usability cycles.}
      \resumeItem{Improved task completion by 33\% and reduced navigation errors by 40\%, with instructors projecting a 25\% reduction in solo car trips if deployed.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Crossing Cafe – Full-Stack Restaurant Website (Team Project)} \emph{\textbar{} HTML, CSS, JavaScript, SQLite, UX Interviews}}
    {Mar. 2024 -- May 2024}
    \resumeItemListStart
      \resumeItem{A local cafe lacked a modern web presence for menu discovery and order clarity, increasing in-store friction during rush periods.}
      \resumeItem{Partnered with a 4-person team to deliver a responsive website grounded in stakeholder requirements and customer workflows.}
      \resumeItem{Conducted structured interviews with owners and customers, converted findings into user stories, and implemented persistent menu and order-tracking using \textbf{SQLite}.}
      \resumeItem{Delivered an MVP that centralized menu updates, reduced ordering confusion, and demonstrated a scalable data-backed ordering workflow.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Blockopoly – Online Multiplayer Digital Card Game} \emph{\textbar{} React, TypeScript, Docker, AWS}$|$
    \href{https://playblockopoly.com}{Live Demo}}{Jun. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Real-time multiplayer web games often break on refresh and struggle with low-latency synchronization across players.}
      \resumeItem{Architect a production-ready system supporting rooms, reconnects, and synchronized turn-based state.}
      \resumeItem{Designed a \textbf{Ktor} backend with \textbf{Redis} for ephemeral state and pub/sub, and shipped real-time updates via \textbf{Server-Sent Events (SSE)} while building a drag-and-drop \textbf{React + TypeScript} UI.}
      \resumeItem{Eliminated polling latency, improved session stability across reloads, and established a scalable blueprint for turn-based multiplayer experiences.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Wishlist – Collaborative Gifting Platform} \emph{\textbar{} React, Go, gRPC, PostgreSQL, Docker}}
    {Jan. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Group gifting coordination lacked transparency, progress tracking, and shared context across friends and families.}
      \resumeItem{Build a full-stack wishlist product enabling users to create, share, and track gifting progress with social signals.}
      \resumeItem{Implemented a service-oriented \textbf{Go + gRPC} backend with \textbf{PostgreSQL}, structured modular React components, and Dockerized services for local-to-cloud parity.}
      \resumeItem{Delivered a maintainable architecture enabling rapid iteration on features like gifting history, friend sorting, and progress-based goals.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Dear Days – Family Event \& Birthday Calendar} \emph{\textbar{} Next.js, Prisma, Tailwind, Google OAuth}}
    {Jul. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Families and groups frequently miss birthdays and special events due to fragmented calendars and weak reminder workflows.}
      \resumeItem{Design a centralized, emotionally engaging system to track special days with simple sharing and clean data models.}
      \resumeItem{Built a \textbf{Next.js} application with \textbf{Prisma} ORM, Google OAuth, and Bento-grid dashboards, using interviews with 6 families to refine onboarding and event-entry flows.}
      \resumeItem{Created a scalable product foundation with strong retention hooks and normalized schemas that support expansion to nationwide multi-family use.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Storybot – Reddit-to-Video Automation Platform} \emph{\textbar{} Node.js, Python, FFmpeg, gTTS, Express}}
    {Jul. 2025 -- Present}
    \resumeItemListStart
      \resumeItem{Short-form creators face high friction converting text stories into captioned videos with consistent pacing and narration quality.}
      \resumeItem{Automate scraping, cleaning, narration, captioning, and audio-video composition into a repeatable pipeline.}
      \resumeItem{Built a \textbf{Node + Python} workflow using \textbf{FFmpeg} and \textbf{gTTS}, defining modular steps for story ingestion, caption overlay, background selection, and batch processing.}
      \resumeItem{Reduced production time from 20+ minutes to under 2 minutes per video while maintaining caption alignment and audio clarity.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{NBA Shot Trends Analysis – 3D Court Visualization} \emph{\textbar{} R, tidyverse, ggplot2, Quarto, GitHub}}
    {Feb. 2025 -- May 2025}
    \resumeItemListStart
      \resumeItem{Coaches and fans lacked a clear, visual narrative for how shot selection shifted across the modern NBA era.}
      \resumeItem{Analyze 300k+ NBA shots (2003--2023) to identify spatial and temporal trends, including player-specific comparisons.}
      \resumeItem{Cleaned and engineered high-volume data using \textbf{tidyverse}, mapped \texttt{loc\_x}/\texttt{loc\_y} to court zones, and generated 3D visual outputs in \textbf{Quarto}.}
      \resumeItem{ Produced an instructor-reviewed report and reproducible workflow highlighting measurable increases in three-point dependency over time.}
    \resumeItemListEnd

    \resumeProjectHeading
  {\textbf{OCamShips (OCaml Battleship Game)} $|$ \emph{OCaml, JavaScript, OUnit, Bisect\_ppx} $|$ 
  \href{https://github.com/stphnmade/ocamlbattleships}{GitHub} $|$ 
  \href{https://stphnmade.github.io/ocamlbattleships/}{Live Demo}}{Feb. 2022 -- May 2022}
\resumeItemListStart
  \resumeItem{Engineered a full Battleship game in OCaml with a GUI state machine (placement, battle loop, win logic) and a rules engine enforcing valid ship placement, collision detection, and hit/sunk transitions.}
  \resumeItem{Implemented the board using a red-black tree keyed by coordinate pairs and developed multi-level AI, including a Monte Carlo-style weighted targeting algorithm for intelligent shot selection.}
  \resumeItem{Deployed a browser edition via GitHub Pages and achieved 90\%+ test coverage on core modules using OUnit and bisect\_ppx.}
\resumeItemListEnd


\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small \item {
    \textbf{Programming Languages}{: Python, Java, JavaScript, TypeScript, Go, Kotlin, C++, OCaml, R} \\
    \textbf{Frameworks \& Libraries}{: React, Next.js, Node.js, Express, Tailwind CSS, Prisma, Ktor, Server-Sent Events (SSE)} \\
    \textbf{Databases \& Infrastructure}{: PostgreSQL, SQLite, Redis, Docker, AWS, gRPC, Git} \\
    \textbf{Platforms \& Tools}{: Jamf, Salesforce, Google Admin, TDX, Office 365, OneDrive, Windows, macOS, Figma, Balsamiq, Quarto, FFmpeg}
  }
\end{itemize}

%-------------------------------------------
\end{document}
